High resolution, annual maps of field boundaries for  smallholder-dominated croplands at national scales

### 2021-10-16 inst/manuscript/manuscript.Rmd
Proper section headers added for conclusion

## Conclusion
This work demonstrates a proof of concept for developing high resolution, annual maps of field boundaries in smallholder-dominated croplands at national to regional scales.  The approach we used to develop these maps includes a novel procedure for compositing daily PlanetScope imagery, and follows recommended best practices for training and assessing machine learning models [@ElmesAccountingtrainingdata2020]. Using PlanetScope data enabled us to make a country-wide, high-resolution, two-season catalog of imagery for a single year, even over areas with frequent cloud cover. Methods to assess labeller accuracy and to create consensus labels helped to  minimize training label errors, which in turn substantially improved the accuracy of the mapping model. Model performance was further enhanced by using an active learning framework, which selects the most informative training sample. This mapping approach can be readily updated to integrate improvements, such as newer machine learning models.

>>>>

# Conclusion
This work demonstrates a proof of concept for developing high resolution, annual maps of field boundaries in smallholder-dominated croplands at national to regional scales.  The approach we used to develop these maps includes a novel procedure for compositing daily PlanetScope imagery, and follows recommended best practices for training and assessing machine learning models [@ElmesAccountingtrainingdata2020]. Using PlanetScope data enabled us to make a country-wide, high-resolution, two-season catalog of imagery for a single year, even over areas with frequent cloud cover. Methods to assess labeller accuracy and to create consensus labels helped to  minimize training label errors, which in turn substantially improved the accuracy of the mapping model. Model performance was further enhanced by using an active learning framework, which selects the most informative training sample. This mapping approach can be readily updated to integrate improvements, such as newer machine learning models.
